---
title: "fourT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fourT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fourT)
```
## Introduction

What does this package do
What are the various workflows (or just idela workflow)
What is the documentation supported in package
What is the structure of the package
 - dependencies
 - how cohort functions generalize individual patient functions
How did I develop this package
 - doing version control in github
    -- show a bit of my github + r workflow
    -- how can this be more helpful when it's not just one person using it
    
Full walkthrough on package use


  

```{r, include = FALSE}
#x_0 <- read_dexcom("~/Desktop/R #Workspace/4T/fourT/vignettes/4T.399_Clarity_Export_00123_Doe_John_2024-05-01_162849.csv", F)
#x_1 <- compute_wear_time(x_0)
#x_2 <- compute_agp(x_0, 1)
#x_3 <- compute_gmi(x_0, 1)
#x_4 <- compute_avg_glucose(x_0, 1)
```

One can read a patient file as follows ...
```{r, message = FALSE}
#read_dexcom(filepath, F)
#View(read_dexcom(filepath, F))
```



